\paperTitle

### 2014-05-12 doc/icml2014/assumption-proof.tex
Updated sigma_max, sigma_min to be sigma_1, sigma_k

  Then, for the unfolding $\{c\}$, we get 
  \begin{align*}
    \sigma_{\min}(\mYpp{c}{\Pa(c)}\munf{I}) &\ge \max_{i\in[\ell]}\{\sigma_{\min}(Z_{\sC_i}\munf{I_i})\},
  \end{align*}
  where $i$ is the subset of $I$ present in clique $\sC_i$.
\end{lemma} 
\begin{proof}
Without loss of generality, let $\sC \eqdef \{c\} \union \Pa(h_c)$ be a clique
  in the graph $\sG$.
If instead $\sC \subseteq \sC_1 \union \sC_2$ for some $\sC_1, \sC_2 \in
\sG$, then $Z_{\sC}$ is the marginalization of some $Z_{\sC_1 \union \sC_2}$
(which may not be a parameter in our model).

\lemmaref{tensor-projection} states that when a tensor, $Z_{\sC_1 \union
\sC_2}$, is projected by a non-zero vector $v$ (in this case, $\ones$),
then the singular values of the projection $Z_\sC$ are preserved along
any unfolding $I$ of $Z_\sC$:
\begin{align*}
  \sigma_{\min}(Z_{\sC}\munf{I}) &\ge \sigma_{\min}(Z_{\sC_1 \union \sC_2}\munf{I})v_{\min} \\
  \sigma_{\min}(Z_{\sC_1 \union \sC_2}\munf{I}) &\ge
  \sigma_{\min}(Z_{\sC}\munf{I})v_{\max}\inv.
\end{align*}

In this case, we get that $\sigma_{\min}(Z_{\sC_1 \union \sC_2}\munf{I})
= \sigma_{\min}(Z_{\sC}\munf{I})v_{\max}\inv$.

@@

\theoremref{tensor-multiplication} shows that for any two tensors $A,
  B$ and an index set $C$, the unfoldings $I$ of $A \times_C B$ are full
  rank when the projected unfoldings $I_A$ of $A$ and $I_B$ of $B$ are
  full rank:
\begin{align*}
  \sigma_{\min}( (A \times_C B)\munf{I} )
    &\ge \sigma_{\min}(A\munf{I_A}) \sigma_{\min}(B\munf{I_B}).
\end{align*}

@@

Next, we turn to the question of the sample complexity of estimating
$\mOpp{v}{i}$, which depends mainly on smallest singular value,
$\sigma_{\min}(\mOpp{v}{i})$.

@@

Let $h_t$ be the unique parent of $x_v$, as above.
Let $h_1 \succ h_2 \cdots \succ h_t$ be a topological ordering of
  variables according to the graph $\sG$.
  Then, the smallest singular value of $\mOpp{v}{1}$ is at least the product of the smallest singular values of $\mYpp{c}{\Pa(h_c)}$.
\begin{align*}
  \sigma_{\min}(\sP) &\ge \sigma_{\min}(\mOpp{v}{t}) 
        \prod_{c \in [t]} \sigma_{\min}(\mYpp{c}{\Pa(h_c)}),
\end{align*}
where the parents $\Pa(h_c)$ are decided by the topological ordering. 
\end{lemma}
\begin{proof}
  The proof follows directly by application of
  \theoremref{tensor-multiplication} to \equationref{expanding-O} and
  \equationref{recursive-step}.
\end{proof}

Finally, using the tensor power method of \citep{anandkumar13tensor}, we
  get the following result on sample complexity.
\begin{theorem}[Sample complexity for $\mOpp{v}{i}$]
  \label{thm:sample-complexity-1}
  Wlog, let $v=1$ and $i=1$. Let $x_1, x_2, x_3$ be three views for
  $h_1$.  
  If 
\begin{align*}
  \|\hat M_{1,2} - M_{1,2}\|_{\op} &\le \epsilon & \|\hat M_{1,2,3} - M_{1,2,3}\|_{\op} &\le \epsilon,
\end{align*}
for some $\epsilon < \half$, then
with probability at least $1 - \delta$,
\begin{align*}
  \|\mOpphat{1}{1} - \mOpp{1}{1}\|_F 
    &\le  \\
    &
      O\left( k 
      \frac{{\pi\oft{1}}_{\max}/{\pi\oft{1}}_{\min}} 
      {(\sigma_{\min}(\mOpp{1}{1}) \sigma_{\min}(\mOpp{1}{2}))^{5/2}} \right) \epsilon.
\end{align*}

Furthermore, if $\sigma_{\min}(\mYpp{c}{\Pa(h_c)}) \le \sigma$ for every
  such
$\mYpp{c}{\Pa(h_c)}$, we get,
\begin{align*}
  \|\mOpphat{1}{1} - \mOpp{1}{1}\|_F 
    &\le 
      O\left( k 
      \frac{{\pi\oft{1}}_{\max}/{\pi\oft{1}}_{\min}} 
      {\sigma^{5t}} \right) \epsilon,
\end{align*}
where $t$ is the length of the topological ordering, $h_1 > \cdots
> h_t$ as defined above.
\end{theorem}
\begin{proof}
  The first statement follows directly from Theorem 5.1 of
  \citet{anandkumar13tensor} by noting that $\|M_{1,2}\|_\op \le 1$ and
  $\|M_{1,2,3}\|_\op \le 1$ (as they represent probability
  distributions). The second statement follows directly from
  \lemmaref{mopp-singular-values}.
\end{proof}

>>>>

  Then, for the unfolding $\{c\}$, we get 
  \begin{align*}
    \sigma_{k}(\mYpp{c}{\Pa(c)}\munf{I}) &\ge \max_{i\in[\ell]}\{\sigma_{k}(Z_{\sC_i}\munf{I_i})\},
  \end{align*}
  where $i$ is the subset of $I$ present in clique $\sC_i$.
\end{lemma} 
\begin{proof}
Without loss of generality, let $\sC \eqdef \{c\} \union \Pa(h_c)$ be a clique
  in the graph $\sG$.
If instead $\sC \subseteq \sC_1 \union \sC_2$ for some $\sC_1, \sC_2 \in
\sG$, then $Z_{\sC}$ is the marginalization of some $Z_{\sC_1 \union \sC_2}$
(which may not be a parameter in our model).

\lemmaref{tensor-projection} states that when a tensor, $Z_{\sC_1 \union
\sC_2}$, is projected by a non-zero vector $v$ (in this case, $\ones$),
then the singular values of the projection $Z_\sC$ are preserved along
any unfolding $I$ of $Z_\sC$:
\begin{align*}
  \sigma_{k}(Z_{\sC}\munf{I}) &\ge \sigma_{k}(Z_{\sC_1 \union \sC_2}\munf{I})v_{k} \\
  \sigma_{k}(Z_{\sC_1 \union \sC_2}\munf{I}) &\ge
  \sigma_{k}(Z_{\sC}\munf{I})v_{\max}\inv.
\end{align*}

In this case, we get that $\sigma_{k}(Z_{\sC_1 \union \sC_2}\munf{I})
= \sigma_{k}(Z_{\sC}\munf{I})v_{\max}\inv$.

@@

\theoremref{tensor-multiplication} shows that for any two tensors $A,
  B$ and an index set $C$, the unfoldings $I$ of $A \times_C B$ are full
  rank when the projected unfoldings $I_A$ of $A$ and $I_B$ of $B$ are
  full rank:
\begin{align*}
  \sigma_{k}( (A \times_C B)\munf{I} )
    &\ge \sigma_{k}(A\munf{I_A}) \sigma_{k}(B\munf{I_B}).
\end{align*}

@@

Next, we turn to the question of the sample complexity of estimating
$\mOpp{v}{i}$, which depends mainly on smallest singular value,
$\sigma_{k}(\mOpp{v}{i})$.

@@

Let $h_t$ be the unique parent of $x_v$, as above.
Let $h_1 \succ h_2 \cdots \succ h_t$ be a topological ordering of
  variables according to the graph $\sG$.
  Then, the smallest singular value of $\mOpp{v}{1}$ is at least the product of the smallest singular values of $\mYpp{c}{\Pa(h_c)}$.
\begin{align*}
  \sigma_{k}(\sP) &\ge \sigma_{k}(\mOpp{v}{t}) 
        \prod_{c \in [t]} \sigma_{k}(\mYpp{c}{\Pa(h_c)}),
\end{align*}
where the parents $\Pa(h_c)$ are decided by the topological ordering. 
\end{lemma}
\begin{proof}
  The proof follows directly by application of
  \theoremref{tensor-multiplication} to \equationref{expanding-O} and
  \equationref{recursive-step}.
\end{proof}

Finally, using the tensor power method of \citep{anandkumar13tensor}, we
  get the following result on sample complexity.
\begin{theorem}[Sample complexity for $\mOpp{v}{i}$]
  \label{thm:sample-complexity-1}
  Wlog, let $v=1$ and $i=1$. Let $x_1, x_2, x_3$ be three views for
  $h_1$.  
  If 
\begin{align*}
  \|\hat M_{1,2} - M_{1,2}\|_{\op} &\le \epsilon & \|\hat M_{1,2,3} - M_{1,2,3}\|_{\op} &\le \epsilon,
\end{align*}
for some $\epsilon < \half$, then
with probability at least $1 - \delta$,
\begin{align*}
  \|\mOpphat{1}{1} - \mOpp{1}{1}\|_F 
    &\le  \\
    &
      O\left( k 
      \frac{{\pi\oft{1}}_{\max}/{\pi\oft{1}}_{\min}} 
      {(\sigma_{k}(\mOpp{1}{1}) \sigma_{k}(\mOpp{1}{2}))^{5/2}} \right) \epsilon.
\end{align*}

Furthermore, if $\sigma_{k}(\mYpp{c}{\Pa(h_c)}) \le \sigma$ for every
  such
$\mYpp{c}{\Pa(h_c)}$, we get,
\begin{align*}
  \|\mOpphat{1}{1} - \mOpp{1}{1}\|_F 
    &\le 
      O\left( k 
      \frac{{\pi\oft{1}}_{\max}/{\pi\oft{1}}_{\min}} 
      {\sigma^{5t}} \right) \epsilon,
\end{align*}
where $t$ is the length of the topological ordering, $h_1 > \cdots
> h_t$ as defined above.
\end{theorem}
\begin{proof}
  The first statement follows directly from Theorem 5.1 of
  \citet{anandkumar13tensor} by noting that $\|M_{1,2}\|_\op \le 1$ and
  $\|M_{1,2,3}\|_\op \le 1$ (as they represent probability
  distributions). The second statement follows directly from
  \lemmaref{mopp-singular-values}.
\end{proof}
